Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-12-01 submit/fix.tex
leaving for day

\begin{abstract}
Through empirical modeling of its observed signal, the peak absolute magnitude of a Type~Ia supernova (SN~Ia) can be accurately determined,
making SNe~Ia  excellent distance indicators.  Improved modeling of SN~Ia absolute magnitudes can account for
further physical
diversity that is expected but not included
in current models, and so consequently can lead to more precise per-object distances with smaller systematic uncertainties.  In this article, we present   
an empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of Ca~II and Si~II, and Si~II velocity
as applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the spectral equivalent widths and the color parameters, to better than 
%-----
$(1-5\times10^{-5})$
%------
confidence.
The color changes allowed by the model are similar to those allowed by the extinction model of  \citet{1999PASP..111...63F} with a free
total-to-selective extinction parameter $R^F$. 
Inspired that with no conditioning our  two-parameter model produces behavior similar to that expected from Galactic dust,
we extend  the model to three color parameters.
In this new case we obtain consistent results for
all the parameters in common,
plus a detection of a third parameter at
%--- table.py
$\sim 90\%$
%-----
confidence.
The 68\% credible interval for the sample effective
%-----
$\langle R^F_{\mathit{\mathit{eff}}}\rangle$ is 2.31 -- 2.69.
%-----
The third parameter is attributed to intrinsic supernova or circumstellar diversity
beyond that tracked by the spectral features and two-parameter dust models.
\end{abstract}

@@

In this article we use the idea that spectral indicators carry information on intrinsic supernova colors at peak magnitude.
This approach is taken by \citet{2011A&A...529L...4C}, who find that after standardization based on Ca and Si features, remaining residual color
variation is consistent with Milky Way dust models.
We accommodate up to  three independent color parameters: the model is constructed such that 
two are assigned as extrinsic processes attributed to dust, and one is attributed to intrinsic supernova
properties.
The data used in this analysis are described in \S\ref{data:sec}.
\added{
The analysis itself is presented as a series of three models of increasing complexity.
\S\ref{modelI:sec}  and  \S\ref{modelII:sec} present the first two models, providing a soft introduction to
our methodology and yielding results to be compared with those from the third model.
That ultimate model and its results are discussed in detail in \S\ref{modelIII:sec}. 
In \S\ref{modelI:sec} we present Model~I, 
a first analysis using spectral features to standardize SN colors
and two additional latent parameters to account for color diversity. 
For Model~II described in \S\ref{modelII:sec}, we add a third latent parameter to the analysis.
Light-curve shape is then added to constitute our final Model~III in \S\ref{modelII:sec}.}
Conclusions are presented in \S\ref{conclusions:sec}.

@@

\section{Model~I: Extrinsic Colors}
\label{modelI:sec}
\added{
We begin by considering Model~I, in which supernova magnitudes  have linear dependence on spectral parameters
and two extrinsic color parameters. The purpose of this section is to introduce some basic concepts of our models,
to show how some of the  model parameters can be expressed in terms of dust-extinction models, and to give Model~I results on dust extinction. 
To avoid repetitiveness,
we refrain from going into full detail on Model~I in deference to Model~III, which is presented in Section~\ref{modelIII:sec}
and is the focus of this article.}

\subsection{Model}
We assume 
that  peak intrinsic ${\hat{U}}{\hat{B}}\hat{V}\hat{R}\hat{I}$ magnitudes of a supernova are linearly dependent
on its
 equivalent widths of the Ca~II H\&K and Si~II~$\lambda$4141 spectral features
$EW_{Ca}$ and $EW_{Si}$,
and the wavelength of the minimum of 
the Si~II~$\lambda6355$ feature $\lambda_{Si}$
around $B$-band peak brightness:
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
The explicit omission of light-curve shape in our model is compensated by its proxy,
$EW_{Si}$, at peak brightness
\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
A grey magnitude offset, $\Delta$, is included for each supernova
to capture 
potential
band-independent intrinsic dispersion, while also absorbing peculiar-velocity errors introduced when converting
fluxes to luminosities.
\added{With this grey offset, the model standardizes colors without reference to an absolute magnitude.
The intrinsic  magnitudes are
\begin{equation}
\begin{pmatrix}
{\hat{U}}\\{\hat{B}}\\{\hat{V}}\\{\hat{R}}\\{\hat{I}}
\end{pmatrix}
=
\Delta \vec{I} +
\begin{pmatrix}
c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} \\
c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  \\
c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} \\
c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} \\
c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}
\end{pmatrix},
\label{ewsiv:eqn}
\end{equation}
where $\vec{I}$ is the Identity vector.
The global parameter vectors\footnote{Global parameters act on each of the five bands: a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
the combination of all components are written as a vector, e.g.\ $\vec{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) )$,.  This 
notationally distinguishes between global versus per-supernova parameters.
}} that describe the SN~Ia population
$\vec{c}$, 
$\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$,  are the intercept
(units of mag) and slopes (units of mag~\AA$^{-1}$)
of the linear relationships that
relate spectral-feature parameters with intrinsic magnitudes.

@@

\added{Except where noted above, we adopt a flat prior for all parameters.

For $N$ supernovae there are $8N$ observables.  There are $3N$ spectral parameters, each of
$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters
(recall the constraint in Eq.~\ref{zero:eqn}),  and $5 \times 7$ global coefficients.
For $N=172$ supernovae, there are 1376 observables and 1064  parameters.

\subsection{Results -- $\vec{\gamma}^0$ and $\vec{\gamma}^1$:  Cofactors the of Extrinsic Color Parameters}
\label{results1:sec}
In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$.
In our model, $g_0$ and $g_1$ are introduced as latent parameters that are related to linear shifts in band magnitudes through
the  coefficients $\vec{\gamma}^0$ and
$\vec{\gamma}^1$.  Otherwise, no physically-motivated suppositions on the properties of $g$ and $\vec{\gamma}$ are imposed.
Attenuation of supernova light due to dust is expected to be mostly captured by the first-order affects described by our linear model.
We  interpret our model $\gamma$'s in terms of
the dust-extinction model of \citet{1999PASP..111...63F} \citepalias[henceforth referred to as][]{1999PASP..111...63F}.

The 68\% credible intervals for $\gamma^0$ and $\gamma^1$ (and all other global parameters) are given in \S\ref{m12results:sec}.}
All elements of the two $\vec{\gamma}$ parameter vectors 
describing intrinsic color
are significantly non-zero.
None of the 20000 links of 
our Monte Carlo chains for $\vec{\gamma}$ come close to the origin, we thus claim detection of the
influence of $g_0$ and $g_1$  on supernova magnitudes
with probability $1-5\times 10^{-5}$.
We thus find a strong signal for a linear 
extrinsic contribution to our model
\begin{equation}
A_X = \gamma^0_X g_0 +  \gamma^1_X g_1.
\end{equation}

\added{Dust-extinction
models are also approximately described by a linear model, here 
using the commonly-used parameterization of $A_V$ and $E(B-V)$
\begin{equation}
A_X = a_X  A_{V} + b_X E(B-V).
\label{f99:eqn}
\end{equation}
}
For example,   the wavelength-dependent model of  \citet{1989ApJ...345..245C} is linear,
though its linearity is lost when integrated over broad-band filters.
For the case of
$R^F=2.5$ and $A^F_V=0.1$ dust attenuating light from the SALT2
\citep{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at ${\hat{B}}$-band peak, the 
\citetalias{1999PASP..111...63F} model
can be approximated with
$\vec{a} = (0.96,   1.00,   1.00,   0.97,   0.77)$ and $\vec{b}=(  1.77,   0.98,   0.12,  -0.50,  -0.53)$.
(The $F$ superscript is used to distinguish parameters of the \citetalias{1999PASP..111...63F} model.)
Over the ranges
 $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$ 
and the wavelengths under consideration here,  the values of the elements of $a$ and $b$ vary by $<5$\%
for the
\citetalias{1999PASP..111...63F} model with
 the largest error in extinction from the linear approximation having amplitude $<0.008$ mag.

@@

For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\zeta}$,
$\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p\vec{\phi}$
are given in Table~\ref{global2:tab}.
In constructing the credible interval of $\sigma_p\vec{\phi}$ 
we set $\vec{\phi} = \text{sign}(\phi_{\hat{I}}) \vec{\phi}$ to break its parity degeneracy;
Figure~\ref{global5:fig} shows there the degenerate solutions are relatively well separated 
in $\sigma_p \phi_{\hat{I}}$.
The effect of spectral parameters on color (as opposed to magnitude)
is shown in the rows of $\alpha_X/\alpha_{\hat{V}}-1$,  $\beta_X/\beta_{\hat{V}}-1$, and  $\eta_X/\eta_{\hat{V}}-1$.
The normalization freedom of $\vec{\gamma}$ is nulled out in the statistic
 $\gamma_X/\gamma_{\hat{V}}-1$.
Note the analogy between these color statistics and the common use of
$R_V^{-1}=A_B/A_V-1$ as an observational descriptor of dust properties.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Parameters& $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
$\alpha_X$
& $0.0059^{+0.0007}_{-0.0008}$
& $0.0033^{+0.0006}_{-0.0007}$
& $0.0029^{+0.0006}_{-0.0006}$
& $0.0026^{+0.0005}_{-0.0005}$
& $0.0041^{+0.0004}_{-0.0005}$
\\
${\alpha_X/\alpha_{\hat{V}}-1}$
& $   1.0^{+   0.2}_{  -0.2}$
& $   0.1^{+   0.1}_{  -0.1}$
&\dots
& $  -0.1^{+   0.0}_{  -0.0}$
& $   0.4^{+   0.2}_{  -0.1}$
\\
$\beta_X$
& $ 0.032^{+ 0.006}_{-0.006}$
& $ 0.021^{+ 0.005}_{-0.005}$
& $ 0.018^{+ 0.005}_{-0.005}$
& $ 0.016^{+ 0.004}_{-0.004}$
& $ 0.008^{+ 0.004}_{-0.004}$
\\
${\beta_X/\beta_{\hat{V}}-1}$
& $  0.79^{+  0.29}_{ -0.19}$
& $  0.16^{+  0.11}_{ -0.08}$
&\dots
& $ -0.12^{+  0.04}_{ -0.04}$
& $ -0.58^{+  0.11}_{ -0.17}$
\\
$\eta_X$
& $0.0022^{+0.0011}_{-0.0011}$
& $0.0024^{+0.0009}_{-0.0010}$
& $0.0027^{+0.0008}_{-0.0008}$
& $0.0025^{+0.0007}_{-0.0007}$
& $0.0018^{+0.0006}_{-0.0006}$
\\
${\eta_X/\eta_{\hat{V}}-1}$
& $ -0.19^{+  0.17}_{ -0.28}$
& $ -0.12^{+  0.09}_{ -0.15}$
&\dots
& $ -0.06^{+  0.06}_{ -0.04}$
& $ -0.33^{+  0.10}_{ -0.10}$
\\
$\zeta_X$
& $ -0.06^{+  0.05}_{ -0.04}$
& $ -0.09^{+  0.04}_{ -0.04}$
& $ -0.12^{+  0.04}_{ -0.04}$
& $ -0.09^{+  0.03}_{ -0.03}$
& $ -0.14^{+  0.03}_{ -0.03}$
\\
${\zeta_X/\zeta_{\hat{V}}-1}$
& $ -0.45^{+  0.20}_{ -0.33}$
& $ -0.26^{+  0.11}_{ -0.18}$
&\dots
& $ -0.20^{+  0.05}_{ -0.07}$
& $  0.22^{+  0.23}_{ -0.13}$
\\
$\gamma^0_X$
& $ 68.29^{+  2.97}_{ -2.92}$
& $ 54.90^{+  2.49}_{ -2.56}$
& $ 40.89^{+  2.38}_{ -2.47}$
& $ 30.95^{+  2.13}_{ -2.25}$
& $ 22.34^{+  2.05}_{ -2.16}$
\\
${\gamma^0_X/\gamma^0_{\hat{V}}-1}$
& $  0.67^{+  0.05}_{ -0.05}$
& $  0.34^{+  0.03}_{ -0.03}$
&\dots
& $ -0.24^{+  0.01}_{ -0.01}$
& $ -0.45^{+  0.03}_{ -0.03}$
\\
$\gamma^1_X$
& $-10.15^{+  4.45}_{ -4.49}$
& $ -6.81^{+  3.88}_{ -3.82}$
& $-15.06^{+  3.42}_{ -3.39}$
& $-14.88^{+  3.01}_{ -3.00}$
& $-15.91^{+  2.90}_{ -2.86}$
\\
${\gamma^1_X/\gamma^1_{\hat{V}}-1}$
& $ -0.32^{+  0.16}_{ -0.21}$
& $ -0.55^{+  0.13}_{ -0.20}$
&\dots
& $ -0.01^{+  0.05}_{ -0.04}$
& $  0.06^{+  0.14}_{ -0.10}$
\\
$\sigma_p \phi_X$
& $ 0.024^{+ 0.009}_{-0.009}$
& $-0.018^{+ 0.007}_{-0.007}$
& $-0.027^{+ 0.006}_{-0.006}$
& $-0.010^{+ 0.006}_{-0.006}$
& $ 0.022^{+ 0.006}_{-0.006}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the global fit parameters of Model~III in \S\ref{modelIII:sec}.\label{global3:tab}}
\end{table}

@@

\subsubsection{Results for the Latent Extrinsic Parameters $g_0$, $g_1$}
\label{g0g1:sec}
The vector
$\vec{\gamma}^0$ describes color changes for an effective $R^F_{\mathit{eff}}=2.40$ dust, as shown 
In  \S\ref{results3gamma:sec}.
Hence, the per-supernova parameter $\gamma^0_{\hat{V}} g_0$ is associated with the $\hat{V}$-band
extinction for a constant $R^F=2.40$.
}
Figure~\ref{k0_med:fig} shows the histogram of
per-supernova
median values
from the Monte Carlo chains
and the  stack of the posteriors of all supernovae  for $\gamma^0_{\hat{V}} g_0$ 
relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} g_0|_0$.
(Subtracting the value of the one supernova suppresses correlated errors common to all supernovae.)
The distributions are non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
with
simulations based on expected dust distributions
within galaxies and the distribution of galaxy orientations with respect to the observer,
which determine column densities along the lines of sight toward supernovae that are consistent with observations
\citep{1998ApJ...502..177H, 2007ApJ...659..122J}.  
We emphasize that unlike other analyses,
this distribution is given by the data, and so is not dependent on any knowledge or prior
for the distribution of dust extinction the SN population is expected to suffer.

@@

There are $>2 \sigma$ correlations between our extrinsic color-excess parameters $g_0$, $g_1$
and the input features  $EW_{Ca}$,
$EW_{Si}$, and $x_1$. 
Given the association
of  $g$ with dust-extinction parameters, this implies that the host environment and the input features are connected.
The correlation between $EW_{Si}$ and host has  already been noted \citep{2011ApJ...734...42N}.
There is a lack of correlation between  $g_0$, $g_1$ and  our velocity parameter $\lambda_{Si}$.
This contrasts with studies of high-velocity features (HVF) identified using
Si~II~$\lambda$6355 that find correlations with host galaxy properties
\citep[e.g.][]{2014MNRAS.444.3258M, 2015MNRAS.446..354P, 2015ApJS..220...20Z}.
The population and properties of HVF SNe within the SNfactory sample will be presented in \citep{2018lin}.
The correlation of $x_1$ with with host-galaxy (including dust) properties is  well established 
\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.

>>>>

\begin{abstract}
Through empirical modeling of its observed signal, the peak absolute magnitude of a Type~Ia supernova (SN~Ia) can be accurately determined,
making SNe~Ia  excellent distance indicators.  Improved modeling of SN~Ia colors and magnitudes can account for
further physical
diversity that is expected but not included
in current models, and so consequently can lead to more precise per-object distances with smaller systematic uncertainties.  In this article, we present   
an empirical model for SN~Ia peak colors with
\added{three color parameters and dependence on the equivalent widths of Ca~II and Si~II, the Si~II velocity,
and the light-curve shape.
This model is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the observable features and on the three color parameters.
The color changes allowed by two of the color parameters are similar to those allowed by the extinction model of  \citet{1999PASP..111...63F}. 
Correspondingly the sample has an effective value of $R^F_{\mathit{eff}} \sim 2.40$, though with a broad distribution of free
total-to-selective extinctions. 
We detect the influence on color by a third parameter at
%--- table.py
$> 99\%$
%-----
confidence.
The third parameter has  unique color characteristics that distinguish it from 
those already  tracked by the spectral features, light-curve shape, and two-parameter dust models.}
\end{abstract}

@@

In this article we use the idea that spectral indicators carry information on intrinsic supernova colors at peak magnitude.
This approach is taken by \citet{2011A&A...529L...4C}, who find that after standardization based on Ca and Si features, remaining residual color
variation is consistent with Milky Way dust models.
We accommodate up to  three independent color parameters: the model is constructed such that 
two are assigned as extrinsic processes attributed to dust, and one is attributed to intrinsic supernova
properties.
The data used in this analysis are described in \S\ref{data:sec}.
\added{
The analysis itself is presented as a series of three models of increasing complexity.
\S\ref{modelI:sec}  and  \S\ref{modelII:sec} present the first two models, providing a soft introduction to
our methodology and yielding results to be compared with those from the third model.
That ultimate model and its results are discussed in detail in \S\ref{modelIII:sec}. 
In \S\ref{modelI:sec} we present Model~I, 
a first analysis using spectral features to standardize SN colors
and two additional latent parameters to account for color diversity. 
For Model~II described in \S\ref{modelII:sec}, we add a third latent color parameter to the analysis.
In \S\ref{modelIII:sec} we present our final Model~III, which  includes light-curve shape as an additional standardization parameter.}
Conclusions are presented in \S\ref{conclusions:sec}.

@@

\section{Model~I: Extrinsic Colors}
\label{modelI:sec}
\added{
We begin by considering Model~I, in which supernova magnitudes  have linear dependence on spectral parameters
and two extrinsic color parameters. The purpose of this section is to introduce some basic concepts of our models,
to show how the two  color terms can be associated with existing dust-extinction models, and to give Model~I results on dust extinction. 
To avoid repetitiveness,
we refrain from going into full detail on the results of Model~I in deference to Model~III, which is presented in Section~\ref{modelIII:sec}.}

\subsection{Model}
We assume 
that  peak intrinsic ${\hat{U}}{\hat{B}}\hat{V}\hat{R}\hat{I}$ magnitudes of a supernova are linearly dependent
on its
 equivalent widths of the Ca~II H\&K and Si~II~$\lambda$4141 spectral features
$EW_{Ca}$ and $EW_{Si}$,
and the wavelength of the minimum of 
the Si~II~$\lambda6355$ feature $\lambda_{Si}$
around $B$-band peak brightness:
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
The explicit omission of light-curve shape in our model is compensated by its proxy,
$EW_{Si}$, at peak brightness
\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
A grey magnitude offset, $\Delta$, is included for each supernova
to capture 
potential
band-independent intrinsic dispersion, while also absorbing peculiar-velocity errors introduced when converting
fluxes to luminosities.
\added{With this grey offset the model standardizes colors, not absolute magnitude.
The intrinsic  magnitudes are
\begin{equation}
\begin{pmatrix}
{\hat{U}}\\{\hat{B}}\\{\hat{V}}\\{\hat{R}}\\{\hat{I}}
\end{pmatrix}
=
\Delta \vec{I} +
\begin{pmatrix}
c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} \\
c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  \\
c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} \\
c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} \\
c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}
\end{pmatrix},
\label{ewsiv:eqn}
\end{equation}
where $\vec{I}$ is the Identity vector.
The global parameter vectors\footnote{Global parameters act on each of the five bands: a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
the combination of all components are written as a vector, e.g.\ $\vec{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) $.  The
band subscript or arrow
notationally identify global parameters, in contrast with the per-supernova parameters.
}} that describe the SN~Ia population
$\vec{c}$, 
$\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$,  are the intercept
(units of mag) and slopes (units of mag~\AA$^{-1}$)
of the linear relationships that
relate spectral-feature parameters with intrinsic magnitudes.

@@

\added{All parameters not  otherwise noted above have flat priors.

For $N$ supernovae there are $8N$ observables.  There are $3N$ spectral parameters, each of
$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters
(recall the constraint in Eq.~\ref{zero:eqn}),  and there are $5 \times 7$ global coefficients.
For $N=172$ supernovae, there are 1376 observables and 1064  parameters.

\subsection{Results for the Extrinsic Latent Parameter Cofactors  $\vec{\gamma}^0$ and $\vec{\gamma}^1$:  }
\label{results1:sec}
In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$.
In our model, $g_0$ and $g_1$ are introduced as latent parameters that are related to linear shifts in band magnitudes through
the  coefficients $\vec{\gamma}^0$ and
$\vec{\gamma}^1$.  Otherwise, no physically-motivated suppositions on the properties of $g$ and $\vec{\gamma}$ are imposed.
Since dust extinction is a dominant determinant of supernova colors that is often described by a 2-parameter linear model, we expect
for our two extrinsic color terms to capture the effects of dust.
We  thus interpret our model $\vec{\gamma}$'s in terms of
the dust-extinction model of \citet{1999PASP..111...63F} \citepalias[henceforth referred to as][]{1999PASP..111...63F}.

The 68\% credible intervals for $\vec{\gamma}^0$ and $\vec{\gamma}^1$ (and all other global parameters) are given in \S\ref{m12results:sec}.
All elements of the two $\vec{\gamma}$ parameter vectors 
describing intrinsic color
are significantly non-zero.
None of the 20000 links of 
our Monte Carlo chains for $\vec{\gamma}$ come close to the origin.   We claim detection
with probability $1-5\times 10^{-5}$ a magnitude term in the form of a 5-dimensional vector (for the 5 bands) spanned by two basis vectors
\begin{equation}
\vec{A} = \vec{\gamma}^0 g_0 +  \vec{\gamma}^1 g_1.
\end{equation}

Dust-extinction
models are also approximately described by a linear model, here 
using the commonly-used parameters $A_V$ and $E(B-V)$
\begin{equation}
\vec{A} =\vec{ a}  A_{V} + \vec{b} E(B-V).
\label{f99:eqn}
\end{equation}
}
For example,   the wavelength-dependent model of  \citet{1989ApJ...345..245C} is linear,
though its linearity is lost when integrated over broad-band filters.
For the case of
$R^F=2.5$ and $A^F_V=0.1$ dust attenuating light from the SALT2
\citep{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at ${\hat{B}}$-band peak, the 
\citetalias{1999PASP..111...63F} model
can be approximated with
$\vec{a} = (0.96,   1.00,   1.00,   0.97,   0.77)$ and $\vec{b}=(  1.77,   0.98,   0.12,  -0.50,  -0.53)$.
(The $F$ superscript is used to distinguish parameters of the \citetalias{1999PASP..111...63F} model.)
Over the ranges
 $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$ 
and the wavelengths under consideration here,  the values of the elements of $a$ and $b$ vary by $<5$\%
for the
\citetalias{1999PASP..111...63F} model with
 the largest error in extinction from the linear approximation having amplitude $<0.008$ mag.

@@

For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\zeta}$,
$\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p\vec{\phi}$
are given in Table~\ref{global2:tab}.
In constructing the credible interval of $\sigma_p\vec{\phi}$ 
we set $\vec{\phi} = -\text{sign}(\phi_{\hat{V}}) \vec{\phi}$ to break its parity degeneracy;
Table~\ref{global3:tab} shows there the largest signal-to-noise in
in $\sigma_p \phi_{\hat{V}}$.
The effect of spectral parameters on color (as opposed to magnitude)
is shown in the rows of $\alpha_X/\alpha_{\hat{V}}-1$,  $\beta_X/\beta_{\hat{V}}-1$, and  $\eta_X/\eta_{\hat{V}}-1$.
The normalization freedom of $\vec{\gamma}$ is nulled out in the statistic
 $\gamma_X/\gamma_{\hat{V}}-1$.
Note the analogy between these color statistics and the common use of
$R_V^{-1}=A_B/A_V-1$ as an observational descriptor of dust properties.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Parameters& $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
$\alpha_X$
& $0.0059^{+0.0007}_{-0.0008}$
& $0.0033^{+0.0006}_{-0.0007}$
& $0.0029^{+0.0006}_{-0.0006}$
& $0.0026^{+0.0005}_{-0.0005}$
& $0.0041^{+0.0004}_{-0.0005}$
\\
${\alpha_X/\alpha_{\hat{V}}-1}$
& $   1.0^{+   0.2}_{  -0.2}$
& $   0.1^{+   0.1}_{  -0.1}$
&\dots
& $  -0.1^{+   0.0}_{  -0.0}$
& $   0.4^{+   0.2}_{  -0.1}$
\\
$\beta_X$
& $ 0.032^{+ 0.006}_{-0.006}$
& $ 0.021^{+ 0.005}_{-0.005}$
& $ 0.018^{+ 0.005}_{-0.005}$
& $ 0.016^{+ 0.004}_{-0.004}$
& $ 0.008^{+ 0.004}_{-0.004}$
\\
${\beta_X/\beta_{\hat{V}}-1}$
& $  0.79^{+  0.29}_{ -0.19}$
& $  0.16^{+  0.11}_{ -0.08}$
&\dots
& $ -0.12^{+  0.04}_{ -0.04}$
& $ -0.58^{+  0.11}_{ -0.17}$
\\
$\eta_X$
& $0.0022^{+0.0011}_{-0.0011}$
& $0.0024^{+0.0009}_{-0.0010}$
& $0.0027^{+0.0008}_{-0.0008}$
& $0.0025^{+0.0007}_{-0.0007}$
& $0.0018^{+0.0006}_{-0.0006}$
\\
${\eta_X/\eta_{\hat{V}}-1}$
& $ -0.19^{+  0.17}_{ -0.28}$
& $ -0.12^{+  0.09}_{ -0.15}$
&\dots
& $ -0.06^{+  0.06}_{ -0.04}$
& $ -0.33^{+  0.10}_{ -0.10}$
\\
$\zeta_X$
& $ -0.06^{+  0.05}_{ -0.04}$
& $ -0.09^{+  0.04}_{ -0.04}$
& $ -0.12^{+  0.04}_{ -0.04}$
& $ -0.09^{+  0.03}_{ -0.03}$
& $ -0.14^{+  0.03}_{ -0.03}$
\\
${\zeta_X/\zeta_{\hat{V}}-1}$
& $ -0.45^{+  0.20}_{ -0.33}$
& $ -0.26^{+  0.11}_{ -0.18}$
&\dots
& $ -0.20^{+  0.05}_{ -0.07}$
& $  0.22^{+  0.23}_{ -0.13}$
\\
$\gamma^0_X$
& $ 68.29^{+  2.97}_{ -2.92}$
& $ 54.90^{+  2.49}_{ -2.56}$
& $ 40.89^{+  2.38}_{ -2.47}$
& $ 30.95^{+  2.13}_{ -2.25}$
& $ 22.34^{+  2.05}_{ -2.16}$
\\
${\gamma^0_X/\gamma^0_{\hat{V}}-1}$
& $  0.67^{+  0.05}_{ -0.05}$
& $  0.34^{+  0.03}_{ -0.03}$
&\dots
& $ -0.24^{+  0.01}_{ -0.01}$
& $ -0.45^{+  0.03}_{ -0.03}$
\\
$\gamma^1_X$
& $-10.15^{+  4.45}_{ -4.49}$
& $ -6.81^{+  3.88}_{ -3.82}$
& $-15.06^{+  3.42}_{ -3.39}$
& $-14.88^{+  3.01}_{ -3.00}$
& $-15.91^{+  2.90}_{ -2.86}$
\\
${\gamma^1_X/\gamma^1_{\hat{V}}-1}$
& $ -0.32^{+  0.16}_{ -0.21}$
& $ -0.55^{+  0.13}_{ -0.20}$
&\dots
& $ -0.01^{+  0.05}_{ -0.04}$
& $  0.06^{+  0.14}_{ -0.10}$
\\
$\sigma_p \phi_X$
& $ 0.024^{+ 0.009}_{-0.009}$
& $-0.018^{+ 0.007}_{-0.007}$
& $-0.027^{+ 0.006}_{-0.006}$
& $-0.010^{+ 0.006}_{-0.006}$
& $ 0.022^{+ 0.006}_{-0.006}$
\\
${\phi_X/\phi_{\hat{V}}-1}$
& $-1.898^{+ 0.420}_{-0.611}$
& $-0.333^{+ 0.156}_{-0.181}$
&\dots
& $-0.609^{+ 0.109}_{-0.163}$
& $-1.834^{+ 0.329}_{-0.486}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the global fit parameters of Model~III in \S\ref{modelIII:sec}.\label{global3:tab}}
\end{table}

@@

\subsubsection{Results for the Latent Extrinsic Parameters $g_0$, $g_1$}
\label{g0g1:sec}
The vector
$\vec{\gamma}^0$ describes color changes for an effective $R^F_{\mathit{eff}}=2.40$ dust, as shown 
In  \S\ref{results3gamma:sec}.
Hence, the per-supernova parameter $\gamma^0_{\hat{V}} g_0$ is associated with the $\hat{V}$-band
extinction for a constant $R^F=2.40$.

Figure~\ref{k0_med:fig} shows the histogram of
per-supernova
median values
from the Monte Carlo chains
and the  stack of the posteriors of all supernovae  for $\gamma^0_{\hat{V}} g_0$ 
relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} g_0|_0$.
(Subtracting the value of the one supernova suppresses correlated errors common to all supernovae.)
The distributions are non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
with
simulations based on expected dust distributions
within galaxies and the distribution of galaxy orientations with respect to the observer,
which determine column densities along the lines of sight toward supernovae that are consistent with observations
\citep{1998ApJ...502..177H, 2007ApJ...659..122J}.  
We emphasize that unlike other analyses,
this distribution is given by the data, and so is not dependent on any knowledge or prior
for the distribution of dust extinction the SN population is expected to suffer.

@@

There are $>2 \sigma$ correlations between our extrinsic color-excess parameters $g_0$, $g_1$
and the input features  $EW_{Ca}$,
$EW_{Si}$, and $x_1$. 
Given the association
of  $g$ with dust-extinction parameters, this implies that the host environment and the input features are connected.
The correlations between$EW_{Si}$ and  $EW_{Ca}$  with host have already been noted \citep{2011ApJ...734...42N, 2015MNRAS.451.1973S}.
There is a lack of correlation between  $g_0$, $g_1$ and  our velocity parameter $\lambda_{Si}$.
This contrasts with studies of high-velocity features (HVF) identified using
Si~II~$\lambda$6355 that find correlations with host galaxy properties
\citep[e.g.][]{2014MNRAS.444.3258M, 2015MNRAS.446..354P, 2015ApJS..220...20Z}.
The population and properties of HVF SNe within the SNfactory sample will be presented in \citep{2018lin}.
The correlation of $x_1$ with with host-galaxy (including dust) properties is  well established 
\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
